Topics in Statistical Theory --- Example Sheet 1

### 2020-11-04 distribution_theory/distribution_ES1_handin.tex
progress is being made

\begin{question}
	Construct a non-zero element of $\DD(\RR)$ that vanishes outside $(0, 1)$. Construct a non-zero of $\DD(\RR^n)$ that vanishes outside the ball $B_\eps = \qty{x \in \RR^n : \norm{x} < \eps}$. 
\end{question}

\begin{proof}
	It is well-known that the function 
	\[
	\phi \colon \RR \to \RR \colon x \mapsto \begin{cases}
		0 &\text{if $x \leq 0$}; \\
		e^{-1/x} &\text{if $x > 0$},
	\end{cases}
	\]
	is smooth and vanishes outside $(0, \infty)$. The function $\psi(x) \ceq \phi(x)\phi(1-x)$ is therefore also smooth and vanishes outside $(0, 1)$.

	Since $\psi$ vanishes outside $(0, 1)$, the function $\psi(x/\eps)$ vanishes outside $(0, \eps)$, and therefore the function $\vec x \mapsto \psi(\norm{\vec x}/\eps)$ vanishes outside $B_\eps$. 
\end{proof}

\begin{mdframed}
For both questions 2 and 4, we need the following lemma:
\begin{lemma} \label{lem:distance_compact_closed}
	Let $K, V \subseteq \RR^n$ where $K$ is compact, $V$ is closed, and $K \cap V = \emptyset$. Then there is a nonzero distance between $K$ and $V$, i.e., 
	\[
	\inf_{x \in K, v \in V} \norm{x - v} > 0. 
	\]
\end{lemma}

@@

\begin{question}
	Given $\phi \in \DD(X)$, Taylor's theorem gives
	\[
	\phi(x+h) = \sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x) + R_N(x, h).
	\]
	Prove that $\supp(R_N)$ is contained in some fixed compact $K \subseteq X$ for $\abs{h}$ sufficiently small. Show also that $\pt^\alpha R_N = o(\abs{h}^N)$ uniformly in $x$ for each multi-index $\alpha$, i.e.\ prove 
	\[
	\lim_{\abs{h}\to 0} \frac{\sup_x \abs{\pt^\alpha R_N(x, h)}}{\abs{h}^N} = 0
	\]
	for each multi-index $\alpha$.

	\emph{Hint: you may find it convenient to use the following form of the remainder}
	\[
	R_N(x, h) = \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t},
	\]
	\emph{and note that} $(N+1)! \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!} = (h_1 + \dotsb + h_n)^{N+1}$. 
\end{question}

@@

\begin{question}
	Which elements of $\DD(X)$ can be represented as a power series on $X$? 
\end{question}

\begin{solution}
	It is known that if two power series agree on an open set, they agree on the entire space. Since every $\phi \in \DD(X)$ is identically zero on some open set (outside its support), the only element of $\DD(X)$ with a power series representation is the zero function. 
\end{solution}

\begin{question}
	Prove the $C^\infty$ Urysohn lemma: if $K$ is a compact subset of $X \subseteq \RR^n$, show that one can find a $\phi \in \DD(X)$ such that $0 \leq \phi \leq 1$ and $\phi = 1$ on a neighborhood of $K$. 
\end{question}

\begin{solution}
	Let $K \subseteq X$, then by \cref{lem:distance_compact_closed}, there is a nonzero distance $d$ from $K$ to $\RR^n \setminus X$, so we have neighbourhoods
	\[
	U_1 \ceq \qty{u \in X \mid d(u, K) < \frac d4}, \quad U_2 \ceq \qty{u \in X \mid d(u, K) < \frac{3d}{4}}
	\]
	which is an open neighbourhood of $K$ with $\clos U \subseteq X$.

	 Let $\chi = \ind_{U_2}$. Now let $\psi \in \DD(\RR^n)$ satisfy $\int_{\RR^n} \psi \dd{x} = 1$ and $\supp\psi \subseteq B(0, \frac d4)$. The we compute
	\begin{align*}
		(\chi * \psi)(x) &= \int_{\RR^n} \chi(y) \psi(x - y) \dd{y} = \int_{U_2} \psi(x - y) \dd{y}.
	\end{align*}
	Clearly, $\chi * \psi \in \DD(X)$, and furthermore, we have for $x \in U_1$ that
	\[
	\int_{U_2} \psi(x - y) \dd{y} = \int_{U_2 - x} \psi(z) \dd{z} \overset\star= 1,
	\]
	since $\supp\psi \subseteq B(0, \frac d4) \subseteq U_2 - x$. This proves the claim.
\end{solution}

\begin{question}
	Given $T \in \DD'(X)$, the derivative $\pt^\alpha T$ is defined by
	\[
	\ang{\pt^\alpha T, \phi} = (-1)^\abs{\alpha} \ang{T, \pt^\alpha\phi} \quad \forall \phi \in \DD(X). 
	\]
	Show that $\pt^\alpha T \in \DD'(X)$. If $\ord(T) = m$ what can you say about $\ord(\pt^\alpha T)$? 
\end{question}

\begin{proof}
	Let $K \subseteq X$ be compact and $\phi \in \DD(X)$. Since $T$ is a distribution, we know that there exists constants $C, N$ such that
	\[
	\abs{\ang{T, \phi}} \leq C \sum_{\abs{\beta} \leq N} \sup \abs{\pt^\beta \phi}. 
	\]

	Letting $M \ceq \abs{\alpha}$, we find
		\begin{align*}
		\abs{\ang{\pt^\alpha T, \phi}} &= \abs{\ang{T, \pt^\alpha\phi}} \leq C \sum_{\abs{\beta} \leq N} \sup \abs{\pt^{\alpha + \beta}\phi} \leq C \sum_{\abs{\beta} \leq M + N} \sup \abs{\pt^\beta \phi}.
	\end{align*}
We conclude that $\pt^\alpha T$ is a distribution, and that if $\ord(T) = m$, $\ord(\pt^\alpha T) \leq m + \abs{\alpha}$. 
\end{proof}

\begin{question}
	Given $T \in \DD'(X)$ and $f \in C^\infty(X)$, prove that for each multi-index $\alpha$
	\[
	\pt^\alpha(Tf) = \sum_{\beta \leq \alpha} \binom{\alpha}{\beta} \pt^\beta f \pt^{\alpha - \beta}T
	\]
	in $\DD'(X)$. 
\end{question}

\begin{proof}
	Let $\phi \in \DD(X)$, then by definition we have $\ang{\pt^\alpha(Tf), \phi} = \ang{T, (-1)^\abs{\alpha} f \pt^\alpha\phi}$. Approximate $T$ by a sequence $(\psi_n) \subseteq \DD'(X)$, then we find
	\begin{align*}
	\ang{T, (-1)^{\abs{\alpha}} f \pt^\alpha\phi} &= \lim_{n\to\infty} \ang{\psi_n,  (-1)^{\abs{\alpha}} f \pt^\alpha\phi} = \lim_{n\to\infty}  (-1)^{\abs{\alpha}} \int_X \psi_n(x) f(x) \pt^\alpha\phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \int_X \pt^\alpha (\psi_n(x) f(x)) \phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \int_X \qty(\sum_{\beta \leq \alpha} \binom\alpha\beta\pt^\beta f(x) \cdot \pt^{\alpha - \beta} \psi_n(x)) \phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \sum_{\beta \leq \alpha} \binom\alpha\beta \ang{\pt^\beta f \pt^{\alpha - \beta} \psi_n, \phi} =  \lim_{n\to\infty} \sum_{\beta \leq \alpha} \binom\alpha\beta (-1)^{\abs{\alpha - \beta}} \ang{\psi_n, \pt^\beta f \pt^{\alpha - \beta} \phi} \\
	&= \sum_{\beta \leq \alpha} \binom\alpha\beta (-1)^{\abs{\alpha - \beta}} \ang{T, \pt^\beta f \pt^{\alpha - \beta} \phi} = \sum_{\beta \leq \alpha} \binom\alpha\beta \ang{\pt^\beta f \pt^{\alpha - \beta} T, \phi} \\
	&= \ang*{\sum_{\beta \leq \alpha} \binom{\alpha}{\beta} \pt^\beta f \pt^{\alpha - \beta}T, \phi}. 
	%&= \lim_{n\to\infty} \ang*{\sum_{\abs{\beta} \leq \abs{\alpha}} \binom\alpha\beta \pt^\beta f\cdot \pt^{\alpha - \beta} \psi_n, \phi} = \lim_{n\to\infty} \sum_{\abs{\beta} \leq \abs{\alpha}
	\end{align*}
\end{proof}

\begin{question}
	Let $(x_k)$ be a sequence in $X$ with no limit point in $X$. Consider the family of linear maps
	$u_\alpha \colon \DD(X) \to \CC$ defined by 
	\[ \ang{u_\alpha, \phi} = \sum_{k=1}^\infty \pt^\alpha \phi(x_k)
	 \]
	 for each multi-index $\alpha$. For what $\alpha$ is $u_\alpha \in \DD'(X)$? What is $\ord(u_\alpha)$? 
\end{question}

\begin{solution}
	Let $K \subseteq X$ be compact. Since $(x_k)$ does not have a limit point, only finitely many of the $x_k$ lie in $K$ (otherwise $(x_k)$ would have a subsequence contained in $K$ which would have a convergent subsequence). Without loss of generality, assume that $x_1, \dotsc, x_n \in K$, and $x_{n+1}, x_{n+2}, \dotsc, \notin K$. Now, for any $\phi \in \DD(X)$ with $\supp(\phi) \subseteq K$ we find
	\begin{align*}
		\abs{\ang{u, \phi}} &= \abs{\sum_{k=1}^\infty \pt^\alpha\phi(x_k)} = \abs{\sum_{k=1}^n \pt^\alpha\phi(x_k)} \leq \sum_{k=1}^n \abs{\pt^\alpha \phi(x_k)} \leq n \cdot \sup \abs{\pt^\alpha\phi} \leq n \cdot \sum_{\abs{\beta} \leq \abs{\alpha}} \sup \abs{\pt^\beta \phi}. 
	\end{align*}
	This shows that $u_\alpha \in \DD'(X)$ for any $\alpha$, with $\ord(u_\alpha) \leq \abs{\alpha}$. We claim that this is an equality, i.e., $\ord(u_\alpha) = \abs{\alpha}$. \TODO How to show??
\end{solution}

\begin{question}
	Find the most general solution to the equations
	\begin{enumerate}[(a)]
		\item $u'  = 1$,
		\item $xu' = \delta_0$,
		\item $(e^{2\pi i x} - 1)u' = 0$
	\end{enumerate}
	in $\DD'(\RR)$. 
\end{question}

\begin{solution}
	Let $\phi \in \DD(X)$. 
	\begin{enumerate}[(a)]
		\item If $u' = 1$ then we find 
		\[
		\int_\RR \phi(x) \dd{x} = \ang{1, \phi} = \ang{u', \phi} = -\ang{u, \phi'},
		\]
		so for any $c \in \RR$ we find by partial integration $\ang{u, \phi'} = - \int_\RR\phi(x) \dd{x} = \int_\RR (x + c) \phi'(x) \dd{x}$. From this we deduce that $u = x + c$ for some $c$.

		\item If $xu' = \delta_0$ then we have
		\[
		\phi(0) = \ang{\delta_0, \phi} = \ang{xu', \phi} = \ang{u', x\phi} = \ang{u, -(x\phi)'} = \ang{u, -x\phi' - \phi} %=  \ang{u, -x\phi'} + \ang{u, -\phi}. 
		\]
		Note that the above is satisfied for $u = - \delta_0 + c$ for any constant $c$. \TODO is this the most general solution?

@@

\begin{question}
	Define the distribution $u \in \DD'(\RR^2)$ by the locally integrable function $u(x, y) = \ind_{x \geq y}$. Show that $\pt_x^2   u - \pt_y^2 u = 0$ in $\DD'(\RR^2)$. Can you give a physical interpretation of this result?
\end{question}

\begin{proof}
	Let $f \in \DD(\RR^2)$, then we have
	\begin{align*}
		\ang{\pt_x^2 u - \pt_y^2 u, f} &= \ang{\pt_x^2 u, f}- \ang{\pt_y^2 u, f} = \ang{u, \pt_x^2 f} - \ang{u, \pt_y^2 f} = \ang{u, \pt_x^2 f - \pt_y^2 f} \\
		&\overset\star= \int_{-\infty}^\infty \int_{y}^\infty \pt_x^2 f(x, y) \dd{x}\dd{y} - \int_{-\infty}^\infty \int_{-\infty}^x \pt_y^2 f(x, y) \dd{y} \dd{x} \\
		&= - \int_{-\infty}^\infty \pt_x f(y, y) \dd{y} - \int_{-\infty}^\infty \pt_y f(x, x) \dd{x}
		\\
		&= - \int_{-\infty}^\infty (\pt_xf + \pt_yf)(x, x) \dd{x}.
	\end{align*}
Here, $\star$ follows from Fubini's theorem. 
Define $g(x) = f(x, x)$, then it is easily seen that $g'(x) = \pt_x f(x, x) + \pt_y f(x, x)$, so we find that
\[
\ang{\pt_x^2 u - \pt_y^2 u, f} = 
- \int_{-\infty}^\infty g'(x) \dd{x} = \lim_{x\to -\infty} g(x) - \lim_{x\to\infty} g(x) = 0 - 0 = 0. 
\]
This shows that $\pt_x u - \pt_y u = 0$, or equivalently, that $u$ satisfies the wave equation. 
\end{proof}

\begin{question}
	Compute $\Delta(\norm{x}^{2-n})$ in $\DD'(\RR^n)$ for $n \geq 3$, i.e.\ compute
	\[
	\ang{\Delta (\norm{x}^{2-n}), \phi} = \ang{\norm{x}^{2-n}, \Delta\phi} = \int \frac{\Delta\phi}{\norm{x}^{n-2}} \dd{x}
	\]
	for arbitrary $\phi \in \DD(\RR^n)$. Note that $\norm{x} = (x_1^2 +\dotsb +x_n^2)^{1/2}$ and $\Delta = \sum_i (\pdv{x_i})^2$.

	\emph{Hint:} use $\int\dd{x} = \int_{\norm{x}\leq\eps}\dd{x} + \int_{\norm{x}>\eps}\dd{x}$ and treat each integral separately. 
\end{question}

\begin{solution}
	We follow the hint: let $\eps > 0$, then we first compute
	\[
	\int_{\norm{x} > \eps} \frac{\Delta\phi}{\norm{x}^{n-2}} \dd{x} = \sum_{i=1}^n \int_{\norm{x} > \eps} \frac{\pdv[2]{x_i} \phi}{\norm{x}^{n-2}}\dd{x} = \sum_{i=1}^n \int_{\norm{x} > \eps} \phi \cdot \pdv[2]{x_i} \norm{x}^{2-n} \dd{x}. 
	\]
	Now, it is easily computed that $\pdv{x_i} \norm{x} = \frac{x_i}{\norm{x}}$, and therefore 
	\begin{align*}
	\pdv[2]{x_i} \norm{x}^{2-n} &= \pdv{x_i} (2-n) x_i \norm{x}^{-n} = (2-n) \qty(\norm{x}^{-n} - n x_i^2 \norm{x}^{-n-2}) \\
	&= (n-2)\norm{x}^{-n} \qty(n \qty(\frac{x_i}{\norm{x}})^2 - 1). 
	\end{align*}
\TODO finish
\end{solution}

\begin{question}
	Let $(f_k)$ be the sequence of smooth functions defined by $f_k(x) = \frac1\pi \frac k{(kx)^2 + 1}$. Prove that $f_k \to \delta_0$ in $\DD'(\RR)$. Compute the limits
	\begin{enumerate}[(a)]
		\item $\lim_{k\to\infty} k^2 x e^{-k^2 x^2}$,
		\item $\lim_{k\to\infty} k^3 e^{ikx}$,
		\item $\lim_{k\to\infty} \frac{\sin(kx)}{\pi x}$,
	\end{enumerate}
in $\DD'(\RR)$. 
\end{question}

\begin{solution}
	It is easily seen that every $f_k$ is locally integrable. Furthermore, noting that $\arctan(kx)' = \frac{k}{(kx)^2 + 1}$, we see by the dominated convergence theorem that
	\begin{align*}
		\lim_{k\to\infty}\ang{f_k, \phi} &= \frac1\pi \lim_{k\to\infty} \int_\RR \frac{k}{(kx)^2 + 1} \phi(x) \dd{x} = -\frac1\pi \lim_{k\to\infty} \int_\RR \arctan(kx) \phi'(x) \dd{x} \\
		&= -\frac1\pi \int_\RR \lim_{k\to\infty} \arctan(kx) \phi'(x) \dd{x} = -\frac1\pi \qty(2 \frac\pi2 \int_0^\infty \phi'(x) \dd{x} ) = \phi(0), 
	\end{align*}
which proves $f_k \to \delta_0$.

\begin{enumerate}[(a)]
	\item We have $- (\frac12 e^{-k^2x^2})' = k^2 x e^{-k^2 x^2}$ and therefore
	\begin{align*}
		\lim_{k\to\infty} \int_\RR k^2 x e^{-k^2x^2} \phi(x) \dd{x} &= \frac12 \lim_{k\to\infty}  \int_\RR  e^{-k^2 x^2} \phi'(x) \dd{x} = \frac12 \int_\RR \lim_{k\to\infty} e^{-k^2 x^2} \phi'(x) \dd{x} = 0,
	\end{align*}
so the sequence converges to 0 in $\DD'(\RR)$.

\item We have 
\begin{align*}
	\lim_{k\to\infty}  k^3 \int_\RR e^{ikx} \phi(x) \dd{x} = \lim_{k\to\infty} 2\pi k^3 \Cal F^{-1}[\phi](k). 
\end{align*}
Since $\phi$ is a Schwarz function, its inverse Fourier transform is also a Schwarz function, and in particular $k^3 \Cal F^{-1}[\phi](k) \to 0$ as $k \to \infty$.

\item This sequence converges to $\delta_0$, although I have no idea how to prove it.

\end{enumerate}
\end{solution}

\begin{question}
	Compute the limit
	\[
	\lim_{k\to\infty} \frac12 + \sum_{m=1}^k \cos(\pi m x)
	\]
	in $\DD'(-1, 1)$. 
\end{question}

\begin{solution}
	Note that \[
	f_k(x) \ceq 
	\frac12 + \sum_{m=1}^k \cos(\pi m x) = \frac12\qty(1 + e^{i \pi x} + e^{-i\pi x} + \dotsb + e^{i \pi m x} + e^{-i\pi m x}) = \frac12 \sum_{m=-k}^k (e^{i\pi x})^m.
	\]
	By viewing the last term as a geometric series $\frac12 e^{-ik\pi x} \sum_{m=0}^{2k+1} (e^{ix})^m$ we can compute that 
	\[
	f_k(x) = \frac{\sin((n + \frac12) \pi x)}{2\sin(\frac12\pi x)}. 
	\]
	It can be shown (???) that $f_k \to \delta_0$ in $\DD'(\RR)$. 
\end{solution}

\begin{question}
	We define the \emph{principal value} of $1/x$, written $\prv(1/x)$, by
	\[
	\ang*{\prv(1/x), \phi} = \lim_{\eps \to 0} \int_{\abs{x} > \eps} \frac{\phi(x)}{x} \dd{x} \quad\text{for all $\phi \in \DD(\RR)$}. 
	\]
	Prove that $\prv(1/x) \in \DD'(\RR)$ and that $\ord(\prv(1/x)) = 1$. Show that
	\[
	\lim_{\eps \to 0} \frac{1}{x - i\eps} = \prv\qty(\frac1x) + i\pi \delta_0 \quad\text{in $\DD'(\RR)$}. 
	\]
\end{question}

\begin{proof}
	First we must show that $\prv(1/x)$ is well-defined.  ??
\end{proof}

\begin{question}
	??
\end{question}
\begin{proof}
	??
\end{proof}

\begin{question}
	??
\end{question}

\begin{proof}
	??
\end{proof}

\begin{question}
	Define the distribution $u \in \EE'(\RR^3)$ by the locally integrable function $u(x) = \ind_{\abs{x}\leq 1}$. Prove that $-\sum_i x_i (\pdv{u}{x_i}) = \dd{\sigma_2}$ in $\EE'(\RR^3)$, where $\dd{\sigma_2}$ is the surface element on the sphere $S^2 \subseteq \RR^3$. 
\end{question}

\begin{proof}
	We have
	\begin{align*}
		\ang*{- \sum_i x_i \pdv{u}{x_i}, \phi} &= - \sum_i \ang*{\pdv{u}{x_i}, x_i\phi} = \sum_i \ang*{u, \pdv{x_i}(x_i \phi)} = \ang*{u, \sum_i \pdv{x_i}(x_i\phi)} \\
		&= \int_{\norm{x} \leq 1} \sum_i \pdv{x_i}(x_i\phi) \dd{x}
	\end{align*}
\end{proof}
\end{document}

>>>>

\begin{mdframed}
For both question 2, we need the following lemma:
\begin{lemma} \label{lem:distance_compact_closed}
	Let $K, V \subseteq \RR^n$ where $K$ is compact, $V$ is closed, and $K \cap V = \emptyset$. Then there is a nonzero distance between $K$ and $V$, i.e., 
	\[
	\inf_{x \in K, v \in V} \norm{x - v} > 0. 
	\]
\end{lemma}

@@

\setcounter{question}{1}
\begin{question}
	Given $\phi \in \DD(X)$, Taylor's theorem gives
	\[
	\phi(x+h) = \sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x) + R_N(x, h).
	\]
	Prove that $\supp(R_N)$ is contained in some fixed compact $K \subseteq X$ for $\abs{h}$ sufficiently small. Show also that $\pt^\alpha R_N = o(\abs{h}^N)$ uniformly in $x$ for each multi-index $\alpha$, i.e.\ prove 
	\[
	\lim_{\abs{h}\to 0} \frac{\sup_x \abs{\pt^\alpha R_N(x, h)}}{\abs{h}^N} = 0
	\]
	for each multi-index $\alpha$.

	\emph{Hint:} you may find it convenient to use the following form of the remainder
	\[
	R_N(x, h) = \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t},
	\]
	and note that $(N+1)! \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!} = (h_1 + \dotsb + h_n)^{N+1}$. 
\end{question}

@@

\setcounter{question}{3}
\begin{question}
	Find the most general solution to the equations
	\begin{enumerate}[(a)]
		\item $u'  = 1$,
		\item $xu' = \delta_0$,
		\item $(e^{2\pi i x} - 1)u' = 0$
	\end{enumerate}
	in $\DD'(\RR)$. 
\end{question}

\begin{solution}
	Let $\phi \in \DD(X)$. 
	\begin{enumerate}[(a)]
		\item It is clear that $x' = 1$ in the distributional sense, since for any test function $\phi$ we have
		\[
		\ang{x', \phi} = -\ang{x, \phi'} = - \int_\RR x \phi'(x) \dd{x} = \int_\RR \phi(x)\dd{x} = \ang{1, \phi}. 
		\]
		Therefore, the equation $u' = 1$ is equivalent to the equation $(u - x)' = 0$. We know that this implies that $u - x = c$ for some constant $c \in \CC$, so the most general solution is $u = x + c$.

		\item If $xu' = \delta_0$ then we have
		\[
		\phi(0) = \ang{\delta_0, \phi} = \ang{xu', \phi} = \ang{u', x\phi} = \ang{u, -(x\phi)'} = \ang{u, -x\phi' - \phi} %=  \ang{u, -x\phi'} + \ang{u, -\phi}. 
		\]
		Note that the above is satisfied for $u = - \delta_0 + c$ for any constant $c\in \CC$.

		I do not know if this is the most general solution and/or how one would show this.

@@

\end{document}

### 2020-11-04 topics_statistical_theory/topics_ES1.tex
progress is being made

\begin{proof}
	We have 
	\[
	\PP(\bar X \geq x) \leq \exp(- \frac{nx^2}{2(\sigma^2 + cx)}) \eqqcolon \delta. 
	\]
	Now we just need express $x$ in terms of $\delta$: taking logarithms on both sides we obtain
	\[
	- \frac{nx^2}{2(\sigma^2 + cx)} = \log(\delta) \implies nx^2 = 2(\sigma^2 + cx) \log(1/\delta) \implies nx^2 - 2c\log(1/\delta) x - 2\sigma^2\log(1/\delta) = 0.
	\]

	Using the abc-formula with the fact that $x \geq 0$ yields 
	\begin{align*}
	x &= \frac{2c \log(1/\delta) + \sqrt{4c^2\log^2(1/\delta) + 8n\sigma^2\log(1/\delta)}}{2n} \\
	&= \frac cn \log(1/\delta) + \sqrt{\frac{c^2}{n^2}\log^2(1/\delta) + \frac{2\sigma^2}{n} \log(1/\delta)} \\
	&= ???? 
	\end{align*}
\end{proof}

@@

We verify that $K_\ell$ has order $\ell$: let $j \in \qty{1, \dotsc, \ell - 1}$, then we have
\begin{align*}
	\int_{-\infty}^\infty u^j K_\ell(u) \dd{u} = \sum_{r=0}^{\ell - 1} \frac{(-1)^r H_r(0)}{r!} \int_{-\infty}^\infty u^j \phi^{(r)}(u) \dd{u}.
\end{align*}
Clearly, if $j < r$, integral in the sum vanishes. If $j = r$, the integral yields $r!$. So we have
\[
\int_{-\infty}^\infty u^j K_\ell(u) \dd{u} = (-1)^j H_j(0) + \sum_{r=0}^{j-1} \int_{-\infty}^\infty u^j \phi^{(r)}(u) \dd{u}. 
\]

??
\end{proof}

@@

\begin{question}
	\begin{enumerate}
		\item 	Verify the algebraic identity
		\[
		\phi_\sigma(x-\mu)\phi_{\sigma'}(x-\mu') = \phi_{\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2}}(x - \mu^*) \phi_{(\sigma + \sigma')^{1/2}}(\mu - \mu')
		\]
		where $\mu^* \ceq (\sigma'^2 \mu + \sigma^2\mu') / (\sigma^2 + \sigma'^2)$, and $\phi_\sigma$ is the $N(0, \sigma^2)$ density.

@@

\begin{proof}
	\begin{enumerate}
		\item \TODO
		\item no.
%		We have 
%		\begin{gather*}
%			\phi_{\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2}}(x - \mu^*) \phi_{(\sigma + \sigma')^{1/2}}(\mu - \mu') \\
%			= \frac{1}{2\pi \sigma \sigma'} \exp(-\frac12\qty(\frac{(x - \mu^*)^2(\sigma^2 + \sigma'^2)}{\sigma^2 \sigma'^2} + \frac{(\mu - \mu^*)^2}{\sigma^2 + \sigma'^2})) \\
%			= \frac{1}{2\pi \sigma \sigma'} \exp\qty(-\frac12\qty(\frac{(x - \mu^*)^2(\sigma^2 + \sigma'^2)^2 + \sigma^2 \sigma'^2 (\mu - \mu^*)^2}{\sigma^2 \sigma'^2(\sigma^2 + \sigma'^2)})) \\
%			=  \frac{1}{2\pi \sigma \sigma'}\exp\qty(-\frac12\qty(\frac{
%			x^2(\sigma^2 + \sigma'^2)^2 + (\sigma'^2\mu + \sigma^2\mu')^2 - 2x (\sigma'^2\mu + \sigma^2\mu') (\sigma^2 + \sigma'^2)	
%		}{\sigma^2 \sigma'^2(\sigma^2 + \sigma'^2)}))
%		\end{gather*}
	\end{enumerate}
\end{proof}
\end{document}

>>>>

\begin{proof}
	Define $x^* \ceq \frac{2^{1/2}\sigma}{n^{1/2}} \log^{1/2}(\frac1\delta) + \frac cn \log(\frac 1\delta)$. Then we have
	\[
	(x^*)^2 = \frac{2\sigma^2}{n}\log(\frac1\delta) + \frac{2^{3/2}\sigma c}{n^{3/2}} \log^{3/2}\qty(\frac1\delta) + \frac{c^2}{n^2} \log^2\qty(\frac1\delta),
	\]
	and therefore
	\begin{align*}
	-\frac{n(x^*)^2}{2(\sigma^2 + cx)} &= - \frac{2\sigma^2 \log(\frac1\delta) + 2^{3/2}\sigma c \log^{3/2}(\frac1\delta)/n^{1/2} + c^2 \log^2(\frac1\delta)/n}{2\sigma^2 + 2^{3/2} \sigma c \log^{1/2}(\frac1\delta)/n^{1/2} + 2c^2\log(\frac1\delta)/n} \\
	&= -\log(\frac1\delta) \frac{2\sigma^2 + 2^{3/2} \sigma c/n^{1/2} + c^2\log(1/\delta)/n}{2\sigma^2 + 2^{3/2} \sigma c/n^{1/2} + 2c^2\log(1/\delta)/n} \\
	&\geq -\log(\frac1\delta) = \log(\delta),
	\end{align*}

	so by Bernstein's inequality we have
	\[
	\PP(\bar X \geq x^*) \leq \exp(\log(\delta)) = \delta, 
	\]
	which is what we wanted to prove.

%	We have 
%	\[
%	\PP(\bar X \geq x) \leq \exp(- \frac{nx^2}{2(\sigma^2 + cx)}) \eqqcolon \delta. 
%	\]

	Now we just need express $x$ in terms of $\delta$: taking logarithms on both sides we obtain
	\[
	- \frac{nx^2}{2(\sigma^2 + cx)} = \log(\delta) \implies nx^2 = 2(\sigma^2 + cx) \log(1/\delta) \implies nx^2 - 2c\log(1/\delta) x - 2\sigma^2\log(1/\delta) = 0.
	\]

	Using the abc-formula with the fact that $x \geq 0$ yields 
	\begin{align*}
	x &= \frac{2c \log(1/\delta) + \sqrt{4c^2\log^2(1/\delta) + 8n\sigma^2\log(1/\delta)}}{2n} \\
	&= \frac cn \log(1/\delta) + \sqrt{\frac{c^2}{n^2}\log^2(1/\delta) + \frac{2\sigma^2}{n} \log(1/\delta)} \\
	&\geq \frac cn \log(1/\delta) + \sqrt{\frac{2\sigma^2}{n} \log(1/\delta)}. 
	\end{align*}

So we have ?????
\end{proof}

@@

We verify that $K_\ell$ has order $\ell$: let $j \in \qty{1, \dotsc, \ell - 1}$, then we have
\begin{align*}
	\int_{-\infty}^\infty u^j K_\ell(u) \dd{u} = \sum_{r=0}^{\ell - 1} \frac{(-1)^r H_r(0)}{r!} \int_{-\infty}^\infty u^j H_r(u) \phi(u) \dd{u}.
\end{align*}
Write $u^j = \sum_{k=0}^j c_k H_k(u)$, then the integral will vanish unless $k = r$, so we get
\[
\int_{-\infty}^\infty u^j K_\ell(u) = \sum_{r=0}^{j} (-1)^r c_r H_r(0) = \sum_{r=0}^j c_r H_r(0) = 0^j = 0,
\]
since $H_r(0) = 0$ for $r$ odd. 
%Clearly, if $j < r$, integral in the sum vanishes. If $j = r$, the integral yields $r!$. So we have
%\[
%\int_{-\infty}^\infty u^j K_\ell(u) \dd{u} = (-1)^j H_j(0) + \sum_{r=0}^{j-1} \int_{-\infty}^\infty u^j \phi^{(r)}(u) \dd{u}. 
%\]
%
%??
\end{proof}

@@

\begin{question}
	\begin{enumerate}[(a)]
		\item 	Verify the algebraic identity
		\[
		\phi_\sigma(x-\mu)\phi_{\sigma'}(x-\mu') = \phi_{\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2}}(x - \mu^*) \phi_{(\sigma^2 + \sigma'^2)^{1/2}}(\mu - \mu')
		\]
		where $\mu^* \ceq (\sigma'^2 \mu + \sigma^2\mu') / (\sigma^2 + \sigma'^2)$, and $\phi_\sigma$ is the $N(0, \sigma^2)$ density.

@@

\begin{proof}
	\begin{enumerate}[(a)]
		\item We have
		\begin{align*}
			&\phantom{=\ }\frac{(x-\mu)^2}{\sigma^2} + \frac{(x - \mu')^2}{\sigma'^2} \\
			&= \frac{\sigma'^2(x - \mu)^2 + \sigma^2(x - \mu')^2}{\sigma^2\sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)x^2 - 2 (\sigma'^2 \mu + \sigma^2 \mu')x + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&=  \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^*x) + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^* + \mu^{*2}) - (\sigma^2 + \sigma'^2)\mu^{*2} + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{\sigma'^2 \mu + \sigma^2 \mu'^2 - (\sigma'^2\mu + \sigma^2\mu')^2/(\sigma^2 + \sigma'^2)}{\sigma^2\sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\sigma^2 + \sigma'^2)(\sigma'^2\mu + \sigma^2\mu'^2) - (\sigma'^2\mu + \sigma^2\mu')^2}{\sigma^2 \sigma'^2(\sigma^2 + \sigma'^2)} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{\sigma^2 + \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{((\sigma^2 + \sigma'^2)^{1/2})^2}, 
		\end{align*}
	which proves the claim. 
	\item Let $K = \phi_1$ and define $K_h(x) \ceq h^{-1} K(x/h)$ so $K_h = \phi_h$. Then recall from the lectures that
	\[
	\MISE(\hat f_n) = \frac1n \int_\RR \qty[(\phi_h^2 * \phi_\sigma)(x) - (\phi_h * \phi_\sigma)^2(x)] \dd{x} + \int_{-\infty}^\infty \qty[ (\phi_h * \phi_\sigma)(x) - \phi_\sigma]^2 \dd{x}
	\]
	\end{enumerate}
\end{proof}
\end{document}
